\begin{center}
    \textbf{\Large Next Math Course Info}
\end{center}
\addcontentsline{toc}{chapter}{Next Math Course Info}

Based on your major, you may be trying to place into MATH 106, 107, 108, or 112 for next semester. This section will help you understand which course you need next, as well as what is needed to place and succeed in that course.

\vspace{.5 cm}

If you are still deciding on a major or interested in exploring different major options, \textbf{The A Center} on campus can provide information about the many different majors offered at the University. Visit them at theacenter.arizona.edu or BASC (Bartlett Academic Success Center).

\vspace{.5 cm}

As always, \textbf{your major advisor} is the best person to ask for specific information about which math course to take next.

\vspace{.5 cm}

{\Large \textbf{Math 106: }}{\large \textbf{Exploring and Understanding Patterns, Functions, and Modeling for Elementary Teachers}}

This course is specifically designed for students who are pursuing a career in elementary education. This course cannot be used as a prerequisite for any other mathematics courses including Math 108 or Math 112 (except Math 302A for Elementary Education).

\vspace{.5 cm}

\textbf{Majors:} College of Education

\vspace{.5 cm}

{\Large \textbf{Math 107: }}{\large \textbf{Exploring and Understanding Data}}

The main purpose of this course is to help students understand, interpret, and represent data in a useful way to prepare students for courses in statistics. This course cannot be used as a prerequisite for any other mathematics courses including Math 108 or Math 112.

\vspace{.5 cm}

\textbf{Majors:} College of Social \& Behavioral Science, Psychology BA, and some other majors (ask your major advisor)

\vspace{.5 cm}

{\Large \textbf{Math 108: }}{\large \textbf{Modeling with Algebraic and Trigonometric Functions}}

Using algebraic and trigonometric functions to model real-life situations. This course is designed for Architecture and Speech, Language, \& Hearing Sciences majors only. Prerequisite to Math 113.

\vspace{.5 cm}

\textbf{Majors:} Architecture and Speech, Language \& Hearing Science

\vspace{.5 cm}

{\Large \textbf{Math 112: }}{\large \textbf{College Algebra Concepts and Applications}}

Properties of functions and graphs, linear and quadratic equations, polynomial functions, exponential and logarithmic functions with applications. \textbf{Students are expected to have a graphing calculator.} Prerequisite to Math 113, 116, 119A, 120R, 163 and other courses.

\vspace{.5 cm}

\textbf{Majors:} Most majors require Math 112, including Eller College of Management, College of Science, College of Engineering, College of Nursing