%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; Solving an exponential equation by finding common bases: Linear exponents}
% type problem below this line
Solve for $x$.

$$4^{-x-3}=8$$




%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$x=-\frac{9}{2}$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; Finding the final amount given the original amount and a percentage increase or decrease
}
% type problem below this line
A house on the market was valued at $\$251,000$. After several years, the value increased by $8\%$. By how much did the house's value increase in dollars? What is the current value of the house?






%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line


Increase in value: $\$20,080$


Current house value: $\$271,080$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; 		
Finding the sale price given the original price and percent discount}
% type problem below this line

An item on sale costs $95\%$ of the original price. The original price was $\$45$.
Use calculator to find the sale price.




%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line


The sale price is $\$42.75$.


%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; Finding the sale price without a calculator given the original price and percent discount
}
% type problem below this line


The price of an item has been reduced by $40\%$. The original price was $\$70$. What is the price of the item now?



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

The price is now $\$42$.



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; Finding the total cost including tax or markup
}
% type problem below this line

A laptop has a listed price of $\$609.95$ before tax. If the sales tax rate is $6.5\%$, find the total cost of the laptop with sales tax included.


Round your answer to the nearest cent, as necessary.





%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$\$649.45$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 7.0\theproblem} )\; Finding the original amount given the result of a percentage increase or decrease
}
% type problem below this line

A company has recently been hiring new employees. Today the company has $36\%$ more employees than it did a year ago. If there are currently $51,000$ employees, how many employees did the company have a year ago?





%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$37,500$ employees



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 7.0\theproblem}
\stepcounter{problem}
\end{minipage}}