\chapter*{Module E}
\addcontentsline{toc}{chapter}{Module E}
\setcounter{problem}{1}

\vspace{1 cm}

\noindent \textbf{Module E} will walk you through the properties of exponents, how to work with polynomials, and how to solve quadratic equations using different methods. With the properties of exponents, you will learn how to calculate simple interest, sales prices, and total cost with tax and markups, as well as calculate the starting amount when taking percentages into account. You will also work with adding, subtracting, multiplying, dividing, and factoring polynomials. In addition, you will work more with rational functions, including how to evaluate a rational function and identify the domain of a rational function. You will also learn how to simplify radical expressions and find perfect nth roots. The rest of \textbf{Module E} will take you through graphing quadratic functions and identifying characteristics of the graphs. You will also use the skills you've previously learned about exponents. For support in \textbf{Module E}, we recommend you review \textbf{Lessons 3A - 3D}, which reviewed properties of exponents, and \textbf{Lessons 10A - 10D}, which reviewed properties of radicals and rations exponents. \textbf{Module E} is further supported by \textbf{Lessons 13A - 13D}, which explored rational expressions, \textbf{Lessons 14A - 14D}, which focused ondifferent types of functions and their graphs, and \textbf{Lessons 15A - 15D} and \textbf{16A - 16D}, which focus on factoring and graphing quadratics. 

\vspace{1 cm}
{\large Objectives:}

\vspace{.3 cm}
By the end of this module, students will be able to:
\begin{itemize}
    \item Calculate the percentage increase or decrease. 
    \item Identify characteristics of non-linear functions, including intercepts, behavior, and minima and maxima. 
    \item Graph basic quadratic functions. 
    \item Understand the different properties of exponents and simplify exponential expressions. 
    \item Find the sum, difference, or product of polynomial expressions.
    \item Factor polynomial expressions, with a focus on quadratics. 
    \item Evaluate rational functions and identify domain and range. 
    \item Evaluate radicals and rational exponents.  
    \item Evaluate and graph exponential functions. 
\end{itemize}

\vfill

\hrule

%\vspace{.5 cm}
%\noindent \hspace{1 cm} Notes \dotfill %\pageref{WholeNum_notes} \hspace{1 cm}

%\noindent \hspace{1 cm} Unit Test Practice \dotfill %\pageref{WholeNum_practice} \hspace{1 cm}

\vspace{.5 cm}

\hrule
\vspace{2 cm}
\newpage

\pagestyle{fancy}
\fancyhead[RO,LE]{Module E}


\input{7 Gator/1-6}

\input{7 Gator/7-12}

\input{7 Gator/19-24}

\input{7 Gator/25-30}

\input{7 Gator/31-36}

\input{7 Gator/37-42}

\input{7 Gator/43-48}

\input{7 Gator/49-54}

\input{7 Gator/55-60}

\input{7 Gator/61-66}

\input{7 Gator/67-72}

\input{7 Gator/73-78}

\input{7 Gator/79-84}

\input{7 Gator/85-90}

\input{7 Gator/91-96}

\input{7 Gator/97-102}

\input{7 Gator/103-108}

\input{7 Gator/109-114}

\newpage

\input{7 Gator/Graphs1}

\input{7 Gator/Additional}

\cleardoublepage