\chapter*{Module A}
\addcontentsline{toc}{chapter}{Module A}
\setcounter{problem}{1}

\vspace{1 cm}

\noindent This module focuses on more simplistic order of operations, evaluating expressions, geometry, and Data Analysis. Concepts \textbf{Module A} are supported by \textbf{Lesson 6A - 6D}, which support your learning around data analysis and lessons \textbf{Lesson 7A - 7D}, which are a deeper dive into expressions and the language needed when describing to someone else how you are simplifying them. Additionally, \textbf{Lessons 8A - 8D} are helpful here to help you clearly see how expressions are different than equations.

\vspace{1 cm}
{\large Objectives:}

\vspace{.3 cm}
By the end of this module, students will be able to:
\begin{itemize}
    \item Understand how to write an exponential expression and when to evaluate exponents in Order of Operations. 
    \item Evaluate algebraic expressions using whole numbers. 
    \item Set up and solve word problems using proportions. 
    \item Calculate the volume of a rectangular prism.
    \item Calculate the mean, median, mode, and weighted mean of data sets. 
    \item Understand the properties of integers. 
\end{itemize}

\vfill

\hrule

%\vspace{.5 cm}
%\noindent \hspace{1 cm} Notes \dotfill %\pageref{WholeNum_notes} \hspace{1 cm}

%\noindent \hspace{1 cm} Unit Test Practice \dotfill %\pageref{WholeNum_practice} \hspace{1 cm}

\vspace{.5 cm}

\hrule
\vspace{2 cm}
\newpage

\pagestyle{fancy}
\fancyhead[RO,LE]{Module A}

\input{3 Cobra/1-6}

\input{3 Cobra/7-12}

\input{3 Cobra/13-18}

\input{3 Cobra/19-24}

\input{3 Cobra/25-30}

\input{3 Cobra/31-36}

\input{3 Cobra/37-42}

\input{3 Cobra/additional}

\cleardoublepage