%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 1.0\theproblem} )\; Finding a unit price}
% type problem below this line
The cost for a pack of $25$ pencils is $\$4.75$.

Find the unit price in dollars per pencil.

If necessary, round your answer to the nearest cent.

%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$\$0.19$

%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Word problem on unit rates associated with ratios of whole numbers: Decimal answers}
% type problem below this line
Answer each part. If necessary, round your answers to the nearest hundredth.
\vspace{0.25 cm}

(a) Tom runs $3$ miles in $29$ minutes.

How many miles does he run per minute?
\vspace{0.5cm}

(b)	Salma bought $7$ pounds of sugar for $\$4$.

How many pounds of sugar did she get per dollar?



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

(a) $0.1$ miles per minute
\vspace{0.5cm}

(b) $1.75$ pounds per dollar



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Solving a word problem using a system of linear equations of the form y = mx + b}
% type problem below this line
A phone company offers two monthly plans. Plan A costs $\$15$ plus an additional $\$0.13$ for each minute of calls. Plan B costs $\$28$ plus an additional $\$0.09$ for each minute of calls.\\
(a) For what amount of calling do the two plans cost the same?
\\
\\
(b) What is the cost when the two plans cost the same?
\\

%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

(a) $325$ minutes
(b) $\$57.25$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Converting between temperatures in Fahrenheit and Celsius}
% type problem below this line
Convert $41^{\circ}$F to degrees Celsius.
If necessary, round your answer to the nearest tenth of a degree.
\vspace{0.25cm}

Here are the formulas.
$$C=\frac{5}{9}(F-32)$$
$$F=\frac{9}{5}C+32$$




%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$41^{\circ}\text{F}=5^{\circ}\text{C}$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Converting between metric and U.S. Customary unit systems}
% type problem below this line
An apartment has $110$ square meters of carpeting. How much is this in square feet? Use the following conversion: $1$ square meter is $10.8$ square feet.





%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$1188 \text{ ft}^2$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Converting between compound units: Basic}
% type problem below this line
A cyclist rides his bike at a rate of $27$ miles per hour. What is this rate in miles per minute? How many miles will the cyclist travel in $2$ minutes? Do not round your answers.
\vspace{0.25cm}

Rate: 
\vspace{0.5cm}

Distance traveled in 2 minutes: 



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

Rate: $0.45$ mi/min
\vspace{0.5cm}

Distance traveled in 2 minutes: $0.9$ mi




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}