%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Variable expressions as inputs of functions: Problem type 1}
% type problem below this line
The function $g$ is defined by $g(x) = 2x^2 - 6$.\\

Find $g(3a)$.



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

$$18a^2 - 6$$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; 
Finding outputs of a one-step function that models a real-world situation: Function notation}
% type problem below this line
Bob tutors chemistry. For each hour that he tutors, he earns $30$  dollars. His earnings, $E$ (in dollars), after tutoring for $h$ hours is given by the following function.
$$E(h) = 30h$$
How much does Bob earn if he tutors for $5$ hours?




%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$150$ dollars




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Finding outputs of a two-step function with decimals that models a real-world situation: Function notation}
% type problem below this line
Kaitlin rented a truck for one day. There was a base fee of $\$10.00$, and there was an additional charge of $6$ cents for each mile driven. The total cost, $C$ (in dollars), for driving $x$ miles is given by the following function.
$$C(x) = 10.00 + 0.06x$$
What is the total rental cost if Kaitlin drove $20$ miles?



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$11.20$ dollars




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 6.0\theproblem} )\; Finding inputs and outputs of a two-step function that models a real-world situation: Function notation}
% type problem below this line

Charlie wants to save $\$700$ to buy a TV. He saves $\$19$ each week. The amount, $A$ (in dollars), that he still needs after $w$ weeks is given by the following function.
$$A(w) = 700 - 19w$$

\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line

(a) If Charlie still needs $\$358$, how many weeks has he been saving? \textbf{18 weeks}\\
\vspace{.2cm}

(b) How much money does Charlie still need after $6$ weeks? \textbf{\$586}



%type answer above this line
}%
{
(a) If Charlie still needs $\$358$, how many weeks has he been saving?\\
\vspace{.2cm}

(b) How much money does Charlie still need after $6$ weeks?



%type problem above this line
}
\vfill\hfill
{\scriptsize 6.0\theproblem}
\stepcounter{problem}
\end{minipage}}