\chapter*{Module D}
\addcontentsline{toc}{chapter}{Module D}
\setcounter{problem}{1}

\vspace{1 cm}

\noindent This module focuses on algebraic expressions and linear functions. It takes the skills you have built over the previous modules and applies them to equations, functions, and systems. You will simplify expressions using distribution and combining like terms, setting you up to be able to solve equations that have one or more variable terms. \textbf{Module D} also focuses on linear functions by having you evaluate them at given x-values and graph them in the coordinate place. You will also explore systems of equations, including parallel and perpendicular lines, and setting up and using algebraic reasoning to solve a system of two linear equations in variables. \textbf{Module D} is supported \textbf{Lessons 11A - 11D}, which focus on types of linear functions and graphing linear functions, and \textbf{Lessons 12A - 12D}, which focus on application problems and systems of equations. 

\vspace{1 cm}
{\large Objectives:}

\vspace{.3 cm}
By the end of this module, students will be able to:
\begin{itemize}
    \item Convert compound units and compare unit rates. 
    \item Use Order of Operations with integer values. 
    \item Evaluate algebraic expressions using distribution and combining like terms. 
    \item Solve single- and multi-step equations. 
    \item Write and solve equations representing real-world problems using variables. 
    \item Graph linear functions in the coordinate plane. 
    \item Set up and solve a system of linear equations representing real-world problems.  
\end{itemize}

\vfill

\hrule

%\vspace{.5 cm}
%\noindent \hspace{1 cm} Notes \dotfill %\pageref{WholeNum_notes} \hspace{1 cm}

%\noindent \hspace{1 cm} Unit Test Practice \dotfill %\pageref{WholeNum_practice} \hspace{1 cm}

\vspace{.5 cm}

\hrule
\vspace{2 cm}
\newpage

\pagestyle{fancy}
\fancyhead[RO,LE]{Module D}

\input{6 Panda/1-6}

\input{6 Panda/7-12}

\input{6 Panda/13-18}

\input{6 Panda/19-24}

\input{6 Panda/25-30}

\input{6 Panda/31-36}

\input{6 Panda/37-42}

\input{6 Panda/43-48}

\input{6 Panda/49-54}

\input{6 Panda/55-60}

\input{6 Panda/61-66}

\input{6 Panda/67-72}

\input{6 Panda/73-78}

\input{6 Panda/79-84}

\input{6 Panda/85-90}

\input{6 Panda/91-96}

\input{6 Panda/97-102}

\input{6 Panda/103-108}

\input{6 Panda/115-120}

\input{6 Panda/121-126}

\input{6 Panda/139-144}

\newpage

\input{6 Panda/Graphs1}

\input{6 Panda/Graphs2}

\newpage

\input{6 Panda/Additional}


\cleardoublepage