%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Multiplication with a decimal and a fraction}
% type problem below this line
Evaluate the following.

$$\frac{7}{5} \times 7.95$$

Write your answer as a decimal.





%type problem above this line
\ifbool{answerKey}%
{Step 1: Convert $\frac{7}{5}$ to a decimal.
$$ \frac{7}{5} means 7 divided by 5.
7 \div 5 = 1.4$$
Step 2: Rewrite.
$$1.4 \times 7.95$$
Step 3: Multiply.
$$1.4 \times 7.95 = 11.13$$}
\vfill \textbf{Answer:}
%type answer below this line
$11.13$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Multiplicative property of equality with signed fractions
}
% type problem below this line
Solve for $u$.
$$
-4u = \frac{12}{7}
$$

Simplify your answer as much as possible.



%type problem above this line
\ifbool{answerKey}%
{Step 1: The variable $u$ is multiplied by $-4$, so undo that and isolate $u$; divide both sides by $−4$.
$$\frac{-4u}{-4} = \frac{12}{7} \times \frac{1}{-4} $$
Step 2: Cancel out $−4$ on the left side due to equivalence and rewrite.
$$u = \frac{12}{7 \times -4}$$
Step 3: Multiply.
$$ u = \frac{12}{-28} $$
Step 4: Simplify by dividing with common factors.
$$ u = \frac{12 \div 4}{-28 \div 4} $$
$$u = - frac {3}{7}$$}
\vfill \textbf{Answer:}
%type answer below this line
$u = -\frac{3}{7}$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Writing ratios for real-world situations}
% type problem below this line
There are 11 books on a shelf. 3 of these books are new. The rest of them are used.
\vspace{.2 cm}

(a) What is the ratio of used books to new books?
\vspace{.2 cm}

(b) What is the ratio of used books to all books on the shelf?





%type problem above this line
\ifbool{answerKey}%
{a) Step 1: Find number of used books.
Used books = Total - New books 
$$= 11-3 
= 8$$
Step 2: Set up ratio according to question.
Ratio = Used : New = $8:3$
b) Step 1: Set up ratio
Ratio = Used : All = $8:11$}
\vfill \textbf{Answer:}
%type answer below this line

(a) $8 : 3$

(b) $8 : 11$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Simplifying a ratio of whole numbers: Problem type 1}
% type problem below this line

Write the ratio as a fraction in simplest form, with whole numbers in the numerator and denominator.

\begin{center}
    9 kg : 45 kg
\end{center} 



%type problem above this line
\ifbool{answerKey}%
{Step 1: Set up the ratio as a fraction.
$$\frac {9 kg}{45 kg}$$
Step 2: Cancel out units due to equivalence.
$$\frac {9}{45}$$
Step 3: Divide both numerator and denominator by common factors.
$$\frac {9 \div 9}{45 \div 9}$$
$$\frac{1}{5}$$}
\vfill \textbf{Answer:}
%type answer below this line
$\frac{1}{5}$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\fbox{\begin{minipage}[t]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Simplifying a ratio of decimals}
% type problem below this line

Write the ratio as a fraction in simplest form, with whole numbers in the numerator and denominator.

\begin{center}
    2.7 : 3.6
\end{center}




%type problem above this line
\ifbool{answerKey}%
{Step 1: Set up ratio as fraction.
$$\frac{2.7}{3.6}$$
Step 2: Multiply both numerator and denominator by 10 to convert decimals to whole numbers.
$$\frac{27}{36}$$
Step 3: Divide numerator and denominator by common factors to get to simplest form.
$$\frac{27 \div 9}{36 \div 9}$$
$$\frac{3}{4}$$}
\vfill \textbf{Answer:}
%type answer below this line
$\frac{3}{4}$



%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\fbox{\begin{minipage}[t][2.85 in]{.465 \textwidth}
\index{({ 5.0\theproblem} )\; Multiplicative property of equality with integers
}
% type problem below this line
Solve for $v$. 
$$
30 = -\frac{v}{2}
$$

Simplify your answer as much as possible.



%type problem above this line
\ifbool{answerKey}%
{
\vfill \textbf{Answer:}
%type answer below this line
$v = -60$




%type answer above this line
}%
{}
\vfill\hfill
{\scriptsize 5.0\theproblem}
\stepcounter{problem}
\end{minipage}}%
