\chapter*{Module C}
\addcontentsline{toc}{chapter}{Module C}
\setcounter{problem}{1}

\vspace{1 cm}

\noindent\textbf{Module C} continues with more complex order of operations with signed fractions and decimals, as well as simplifying ratios. Additionally, you will begin to work with square roots and the Pythagorean Theorem. The final concept in \textbf{Module C} is the introduction of points in the coordinate plane, on which we will spend more time when we are in Module D. Concepts in \textbf{Module C} are supported by \textbf{Lessons 9A - 9D}, which focus on evaluating expressions with integers and non-integers and \textbf{Lessons 10A - 10D}, which help you make the connection between radicals and rational exponents. \textbf{Lessons 11A - 11D} and \textbf{Lessons 12A - 12D} do a deep dive into lines and will help you prepare for Module D. 

\vspace{1 cm}
{\large Objectives:}

\vspace{.3 cm}
By the end of this module, students will be able to:
\begin{itemize}
    \item Apply Order of Operations to expressions including decimals.
    \item Write and simplify ratios for real-world scenarios.
    \item Find the root of a perfect square and to use a calculator to approximate a square root value. 
    \item Use ratios to complete unit conversions.
    \item Compare and order real numbers, including integers, rational numbers, and irrational numbers.  
    \item Identify and apply properties of addition and multiplication to real numbers. 
    \item Read and plot points in the coordinate plane.
\end{itemize}

\vfill

\hrule

%\vspace{.5 cm}
%\noindent \hspace{1 cm} Notes \dotfill %\pageref{WholeNum_notes} \hspace{1 cm}

%\noindent \hspace{1 cm} Unit Test Practice \dotfill %\pageref{WholeNum_practice} \hspace{1 cm}

\vspace{.5 cm}

\hrule
\vspace{2 cm}
\newpage

\pagestyle{fancy}
\fancyhead[RO,LE]{Module C}

\input{5 Rhino/1-6}

\input{5 Rhino/7-12}

\input{5 Rhino/13-18}

\input{5 Rhino/19-24}

\input{5 Rhino/25-30}

\input{5 Rhino/31-36}

\input{5 Rhino/37-42}

\input{5 Rhino/43-48}

\input{5 Rhino/additional}

\cleardoublepage