\chapter*{Refresh 1}
\addcontentsline{toc}{chapter}{Refresh 1}
\setcounter{problem}{1}

\vspace{1 cm}

\noindent This module focuses on the foundations of math. It takes you through the operations of addition, subtraction, multiplication, and division of whole numbers, fractions, and decimals. It will also review the basic geometric figures, how to identify units of measure, and rounding rules. Concepts \textbf{Refresh 1} are supported by \textbf{Lessons 2A - 2D}, which review the rounding rules you will need for this module.  

\vspace{1 cm}
{\large Objectives:}

\vspace{.3 cm}
By the end of this module, students will be able to:
\begin{itemize}
    \item Understand place value and how to write numbers in expanded form.
    \item Understand rounding rules and how to approximate values. 
    \item Perform addition, subtraction, multiplication, and division with whole numbers. 
    \item Understand what makes a value a fraction or a decimal and how to convert between the two forms. 
    \item Calculate the perimeter and area of polygons. 
\end{itemize}

\vfill

\hrule

%\vspace{.5 cm}
%\noindent \hspace{1 cm} Notes \dotfill %\pageref{WholeNum_notes} \hspace{1 cm}

%\noindent \hspace{1 cm} Unit Test Practice \dotfill %\pageref{WholeNum_practice} \hspace{1 cm}

\vspace{.5 cm}

\hrule
\vspace{2 cm}
\newpage

\pagestyle{fancy}
\fancyhead[RO,LE]{Refresh 1}

\input{1 Hippo/1-6}

\input{1 Hippo/7-12}

\input{1 Hippo/13-18}

\input{1 Hippo/19-24}

\input{1 Hippo/25-30}

\input{1 Hippo/31-36}

\input{1 Hippo/37-42}

\input{1 Hippo/43-48}

\input{1 Hippo/49-54}

\input{1 Hippo/55-60}

\input{1 Hippo/61-66}

\input{1 Hippo/67-72}

\input{1 Hippo/73-78}

\input{1 Hippo/79-84}

\input{1 Hippo/85-88}

\input{1 Hippo/additional}

\fancyhead{}

\cleardoublepage